\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins

\usepackage{xcolor}
% \usepackage{emoji}
% \usepackage{emoji}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Mariano Maisonnave} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+1(902) 448-5124 \\ Halifax, NS} 
\address{\href{mailto:mariano.maisonnave@dal.ca}{mariano.maisonnave@dal.ca} \\ \href{https://cs.dal.ca/~maisonnave/google-scholar}{cs.dal.ca/$\sim$maisonnave/google-scholar} \\ \href{https://web.cs.dal.ca/~maisonnave/}{cs.dal.ca/$\sim$maisonnave}}  %
% \address{\color{gray}(he/him)}

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\vspace{-0.3cm}     
\begin{rSection}{OBJECTIVE}

{\textbf{Computer science postdoc at Dalhousie University} with 7+ years of training in natural language (NLP) and Machine Learning (ML). 6+ years of teaching Experiencie: worked as Professor, Head of Teaching Assistants and Teaching Assistant in several undergrad courses (most relevant courses: Object-Oriented Programming (6 years) Computer Networking and Embedded Systems (2 years)). \\
 \textbf{Research interests}: Information Extraction, Event Detection and Term Weighting in texts. Familiar with state-of-the-art ML and NLP technologies and libraries (spaCy, HuggingFace, Keras, Scikit-learn, and others). Studied and used causality, time series, and econometric tools. Worked on building interpretable causal graphs from news articles. 
Currently working in high-recall information retrieval.  
}
\vspace{-0.2cm}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Ph.D. in Computer Science} (GPA 9.86/10), Universidad Nacional del Sur, Argentina \hfill {2017 --- 2021}\\
\underline{Thesis}: Variable selection and causal discovery from  newspaper article texts. \href{https://repositoriodigital.uns.edu.ar/bitstream/handle/123456789/5827/MAISONNAVE\%20M._TESIS.pdf?sequence=2&isAllowed=y}{[link (Spanish)]}\\
% Relevant courses: Econometrics, 


\vspace{-0.4cm}

{\bf Computer Systems Engineer} (GPA 8.58/10), Universidad Nacional del Sur, Argentina \hfill {2011 --- 2016}\\
\underline{Final project}: Feature engineering techniques evaluated on supervised learning methods.
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\

\vspace{-0.2cm}
\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SELECTED SKILLS (NOT EXHAUSTIVE)}
\vspace{-0.2cm}
\begin{table}[!ht]
\begin{tabular}{lllllllll}
Python & Java & SQL & Git/Github  & Linux and Bash       & Docker  &  VIM   & Matlplotlib & Pandas    \\
NLTK   & Keras & TensorFlow &    NumPy      &  Jupyter Notebook    & spaCy           &    SciPy   & Scikit-learn  & C       
\end{tabular}
\end{table}
\vspace{-0.6cm}
% Python, NumPy, statsmodels, SciPy, Pandas, Matplotlib, Jupyter Notebook, Scikit-learn, spaCy, NLTK, Keras with TensorFlow, Linux and Bash, Git, Docker, SQL and VIM. 

% Git, Linux and Bash, Keras with TensorFlow, Scikit-learn, Hugging Face, NLTK, , Jupyter, Pandas, Docker, SQL, Numpy, spaCy, and vim.
% \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
% Selected Technical Skills & Python, Git, Linux and Bash, Keras, Scikit-learn, 
% % \\
% % Soft Skills & A, B, C, D\\
% % XYZ & A, B, C, D\\
% \end{tabular}\\
\vspace{-0.2cm}
\end{rSection}


\begin{rSection}{EXPERIENCE}

\textbf{Computer Science Postdoc} \hfill Nov 2021 --- Present\\
Dalhousie University \hfill \textit{Halifax, NS}
    \vspace{-0.2cm}     
 \begin{itemize}
    \itemsep -3pt {} 
     \item Lead computer science researcher in a multidisciplinary project that aims to support text-intensive research in social science through the development of novel computer science tools.
    \vspace{-0.18cm}     
     \item Development and testing of an information retrieval system based on scalable continuous active learning.
    \vspace{-0.18cm}     
     \item Coding, testing and deployment of machine learning-based systems. Presentations at conferences and writing scientific articles. 
    \vspace{-0.1cm}     
    % \item Developed XYZ that did A, B, and C using X, Y, and Z. 
 \end{itemize}
 
\textbf{Teaching} \hfill Oct 2015 --- Present\\
Universidad Nacional del Sur \hfill \textit{Bahía Blanca, Argentina}
    \vspace{-0.2cm}     
 \begin{itemize}
    \itemsep -3pt {} 
     \item Work as teaching assistant, head of teaching assistant and professor of several undergrad courses.
    \vspace{-0.18cm}     
     \item Courses: Computer Networking, Introduction to Object-Oriented Programming, Formal Languages and Automata Theory, Computer Organization  and  Embedded Systems. 

 \end{itemize}
\vspace{-0.2cm}
\end{rSection} 

\begin{rSection}{SELECTED PUBLICATIONS}
\vspace{-1.25em}
\item \textbf{Maisonnave, M}., Delbianco, F., Tohmé, F., Milios, E. and Maguitman, A.G., 2022. \textit{Causal graph extraction from news: a comparative study of time-series causality learning techniques}. PeerJ Computer Science, 8, p.e1066. \href{https://peerj.com/articles/cs-1066/}{[link]}
\vspace{-0.3cm}
\item \textbf{Maisonnave, M}., Delbianco, F., Tohmé, F., Maguitman, A. and Milios, E., 2022. \textit{Detecting ongoing events using contextual word and sentence embeddings}. Expert Systems with Applications, 209, p.118257. \href{https://www.sciencedirect.com/science/article/pii/S0957417422013975}{[link]}
% \vspace{-0.3cm}
% \item \textbf{Maisonnave, M}., Delbianco, F., Tohmé, F. and Maguitman, A., 2021. \textit{Assessing the behavior and performance of a supervised term-weighting technique for topic-based retrieval}. Information Processing \& Management, 58(3), p.102483. \href{https://www.sciencedirect.com/science/article/pii/S0306457320309729}{[link]}
% \vspace{-0.15cm}
\vspace{-0.2cm}
\end{rSection} 
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

% \begin{rSection}{PROJECTS}
% \vspace{-1.25em}
% \item \textbf{Hiring Search Tool.} {Built a tool to search for Hiring Managers and Recruiters by using ReactJS, NodeJS, Firebase and boolean queries. Over 25000 people have used it so far, with 5000+ queries being saved and shared, and search results even better than LinkedIn! \href{https://hiring-search.careerflow.ai/}{(Try it here)}}
% \item \textbf{Short Project Title.} {Build a project that does something and had quantified success using A, B, and C. This project's description spans two lines and also won an award.}
% \item \textbf{Short Project Title.} {Build a project that does something and had quantified success using A, B, and C. This project's description spans two lines and also won an award.}
% \end{rSection} 

%----------------------------------------------------------------------------------------
% \begin{rSection}{Extra-Curricular Activities} 
% \begin{itemize}
%     \item 	Actively write \href{https://www.faangpath.com/blog/}{blog posts} and social media posts (\href{https://www.tiktok.com/@faangpath}{TikTok}, \href{https://www.instagram.com/faangpath/?hl=en}{Instagram}) viewed by over 20K+ job seekers per week to help people with best practices to land their dream jobs. 
%     \item	Sample bullet point.
% \end{itemize}


% \end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{AWARDS AND SCHOLARSHIPS} 
\begin{itemize}
    \item Three-year winner of the Google Latin America Research Award (Google LARA) (2019, 2020 and 2021). Project: ``\textit{Learning Causal Models from Digital Media}.''
    \vspace{-0.2cm}     
    \item Recipient of the Emerging Leaders in the Americas Program (ELAP) scholarship, 2018. Funding for a research stay at Dalhousie University from December 2018 to April 2019.
    \vspace{-0.2cm}     
    \item Recipient of a five-year scholarship to pursue a doctorate in computer science, 2017-2022. Granted by the Argentinian National Scientific and Technical Research Council (CONICET).
    \vspace{-0.2cm}     
    \item Recipient of the Encouragement of Scientific Vocations Scholarship (EVC-CIN), 2015 and 2016. Funding for undergrad students to conduct a part-time research project.
\end{itemize}

\vspace{-0.2cm}
\end{rSection}
% %----------------------------------------------------------------------------------------
% \begin{rSection}{Leadership} 
% \begin{itemize}
%     \item Admin for the \href{https://discord.com/invite/WWbjEaZ}{FAANGPath Discord community} with over 6000+ job seekers and industry mentors. Actively involved in facilitating online events, career conversations, and more alongside other admins and a team of volunteer moderators! 
% \end{itemize}


% \end{rSection}


\end{document}
